Spatial Reasoning and Statistical Graphics

### 2014-10-22 Paper/Draft1/TestingVisualAptitude.Rnw
Code to sanitize latex table names

library(reshape2)
suppressMessages(library(ggplot2))
library(plyr)
suppressMessages(library(gridExtra))
library(xtable)
source(paste(codedir, "Analysis.R", sep=""))
@

>>>>

library(reshape2)
suppressMessages(library(ggplot2))
library(plyr)
suppressMessages(library(gridExtra))
library(xtable)
source(paste(codedir, "Analysis.R", sep=""))

sanitize <- function(x){
  str_replace(gsub("_", ".", x, fixed=T), "Pr\\((.{1,}))", "Pr$(\\1)$")
}

@
